---
title: "Inference HW"
author: "Josh Miller"
format: html
embed-resources: true
---

## Problem 1
```{r}
#| message: false

library(ISLR2)
library(tidyverse)
data(Carseats)

t.test(Carseats$Price, mu = 110)

ggplot(Carseats, aes(x = Price)) +
  geom_histogram(binwidth = 5, fill = "skyblue", color = "white")+
  labs(
    title = "Distribution of Car Seat Prices",
    x = "Price ($)",
    y = "Count"
  ) +
  theme_minimal()

```
Both the histogram and the t-test indicate that the mean price of carseats is not $110. The histogram shows that there is a majority of the data to the right of $110 implying that the true mean price is greater than that. The t-test shows that the mean is $115.795 with a p-value of less than 0.001 this indicates that there is a significant difference between $110 and $115.795. 

## Problem 2

```{r}
t.test(Carseats$CompPrice, conf.level = 0.90)

```
* 90% Confidence Level: 126.2391 to 123.7109
* Sample Mean: 124.975
* Margin of Error: (126.2391 - 123.7109)/2 = 1.2641

## Problem 3

```{r}
library(palmerpenguins)

island_specie_t <- table(penguins$species, penguins$island)
addmargins(island_specie_t)

```
Contingency table indicating the species of Penguin in the y-axis and the island name in the x-axis. The table also includes marginal counts.
